PANCHANGE_data_preprocessing

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
added coping ocir data sets

@@

@@

@@

@@

# glad COPING ocir

```{r coping glad ocir cols}
coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_coping_glad.rds"))
dim(coping.glad.ocir.raw)
colnames(coping.glad.ocir.raw)
```

@@

@@

missigness

@@

>>>>

```{r coping glad gad copy}
if(GLAD == TRUE) {
  coping.phq.raw.id <- coping.glad.phq.raw.id
}
```

@@

```{r coping edgi gad copy}
if(EDGI == TRUE) {
  coping.phq.raw.id <- coping.edgi.phq.raw.id
}
```

@@

```{r coping nbr gad copy}
if(NBR == TRUE) {
  coping.phq.raw.id <- coping.nbr.phq.raw.id
}
```

@@

```{r coping ramp gad copy}
if(RAMP == TRUE) {
  coping.phq.raw.id <- coping.ramp.phq.raw.id
}
```

@@

# COPING: OCI-R

## GLAD
```{r coping glad ocir cols}
coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_coping_glad.rds"))
dim(coping.glad.ocir.raw)
colnames(coping.glad.ocir.raw)
```

@@

```{r coping glad ocir copy}
if(GLAD == TRUE) {
  coping.ocir.raw.id <- coping.glad.ocir.raw.id
}
```

## EDGI
```{r coping edgi ocir cols}
coping.edgi.ocir.raw <- readRDS(file = paste0(data.raw_path, "/edgi/ocir_coping_edgi.rds"))
dim(coping.edgi.ocir.raw)
colnames(coping.edgi.ocir.raw)
```

```{r coping edgi ocir summary labels}
summarytools::dfSummary(
  coping.edgi.ocir.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
```

*Note that the COPING EDGI OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
```{r coping edgi ocir cleaning}
coping.edgi.ocir.raw.id <- coping.edgi.ocir.raw %>%
    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from EDGI prepandemic
    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from EDGI prepandemic
    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from EDGI prepandemic
    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from EDGI prepandemic
    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from EDGI prepandemic
    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from EDGI prepandemic
    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from EDGI prepandemic
    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from EDGI prepandemic
    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from EDGI prepandemic
    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from EDGI prepandemic
    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from EDGI prepandemic
    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from EDGI prepandemic
    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from EDGI prepandemic
    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from EDGI prepandemic
    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from EDGI prepandemic

# Inspect dimensions
dim(coping.edgi.ocir.raw.id)
# Inspect colnames
colnames(coping.edgi.ocir.raw.id)
#Differences
dim(coping.edgi.ocir.raw)[1]-dim(coping.edgi.ocir.raw.id)[1]
```

```{r coping edgi ocir copy}
if(EDGI == TRUE) {
  coping.ocir.raw.id <- coping.edgi.ocir.raw.id
}
```

## NBR
```{r coping nbr ocir cols}
coping.nbr.ocir.raw <- readRDS(file = paste0(data.raw_path, "/nbr/ocir_coping_nbr.rds"))
dim(coping.nbr.ocir.raw)
colnames(coping.nbr.ocir.raw)
```

```{r coping nbr ocir summary labels}
summarytools::dfSummary(
  coping.nbr.ocir.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
```

*Note that the COPING NBR OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
```{r coping nbr ocir cleaning}
coping.nbr.ocir.raw.id <- coping.nbr.ocir.raw %>%
    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from NBR prepandemic
    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from NBR prepandemic
    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from NBR prepandemic
    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from NBR prepandemic
    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from NBR prepandemic
    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from NBR prepandemic
    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from NBR prepandemic
    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from NBR prepandemic
    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from NBR prepandemic
    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from NBR prepandemic
    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from NBR prepandemic
    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from NBR prepandemic
    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from NBR prepandemic
    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from NBR prepandemic
    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from NBR prepandemic

# Inspect dimensions
dim(coping.nbr.ocir.raw.id)
# Inspect colnames
colnames(coping.nbr.ocir.raw.id)
#Differences
dim(coping.nbr.ocir.raw)[1]-dim(coping.nbr.ocir.raw.id)[1]
```

```{r coping nbr ocir copy}
if(NBR == TRUE) {
  coping.ocir.raw.id <- coping.nbr.ocir.raw.id
}
```

## RAMP
```{r coping ramp ocir cols}
coping.ramp.ocir.raw <- readRDS(file = paste0(data.raw_path, "/ramp/ocir_coping_ramp.rds"))
dim(coping.ramp.ocir.raw)
colnames(coping.ramp.ocir.raw)
```

```{r coping ramp ocir summary labels}
summarytools::dfSummary(
  coping.ramp.ocir.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
```

*Note that the COPING RAMP OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
```{r coping ramp ocir cleaning}
coping.ramp.ocir.raw.id <- coping.ramp.ocir.raw %>%
    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from RAMP prepandemic
    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from RAMP prepandemic
    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from RAMP prepandemic
    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from RAMP prepandemic
    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from RAMP prepandemic
    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from RAMP prepandemic
    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from RAMP prepandemic
    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from RAMP prepandemic
    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from RAMP prepandemic
    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from RAMP prepandemic
    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from RAMP prepandemic
    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from RAMP prepandemic
    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from RAMP prepandemic
    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from RAMP prepandemic
    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from RAMP prepandemic

# Inspect dimensions
dim(coping.ramp.ocir.raw.id)
# Inspect colnames
colnames(coping.ramp.ocir.raw.id)
#Differences
dim(coping.ramp.ocir.raw)[1]-dim(coping.ramp.ocir.raw.id)[1]
```

```{r coping ramp ocir copy}
if(RAMP == TRUE) {
  coping.ocir.raw.id <- coping.ramp.ocir.raw.id
}
```

@@

@@

# Inspection
